Is high social class always beneficial for survival? A study of northern Sweden 1801--2013 \footnote{Short; "Is high social class beneficial for survival?"} \footnote{Funding:This work was founded by the Swedish Research Council under grants No 349-2008-6592 No 421-2012-892}

### 2018-10-01 popstud_open.Rmd
Corrections in appendix

```{r exposuretab, message = FALSE, cache = FALSE, results = 'asis'}
##expo <- aggregate(vb[, c("exposure")], by = vb[, c("hisclass", "period", "sex")], FUN = sum)
ex <- with(vb, tapply(exposure, list(period, hisclass, sex), sum))
print(xtable(ex[,,2], label = "tab:womenexp", caption = "Exposure in years by hisclass and period, women.", digits = 0), 
      type = "latex", comment = FALSE)
```

```{r exposuretab2, message = FALSE, cache = FALSE, results = 'asis'}
print(xtable(ex[,,1], label = "tab:menexp", caption = "Exposure in years by hisclass and period, men.", digits = 0), 
      type = "latex", comment = FALSE)
```

@@

```{r deathtab, message = FALSE, cache = FALSE, results = 'asis'}
##expo <- aggregate(vb[, c("exposure")], by = vb[, c("hisclass", "period", "sex")], FUN = sum)
deaths <- with(vb, tapply(event, list(period, hisclass, sex), sum))
print(xtable(deaths[,,2], label = "tab:womendeaths", caption = "Number of deaths by hisclass and period, women.", digits = 0), 
      type = "latex", comment = FALSE)
```

```{r deathtab2, message = FALSE, cache = FALSE, results = 'asis'}
print(xtable(deaths[,,1], label = "tab:mendeaths", caption = "Number of deaths by hisclass and period, men.", digits = 0), 
      type = "latex", comment = FALSE)
```

>>>>

```{r exposuretab, message = FALSE, cache = FALSE, results = 'asis'}
##expo <- aggregate(vb[, c("exposure")], by = vb[, c("hisclass", "period", "sex")], FUN = sum)
ex <- with(vb, tapply(exposure, list(period, hisclass, sex), sum))
print(xtable(ex[,,2], label = "tab:womenexp", caption = "Exposure in years by social class and period, women.", digits = 0), 
      type = "latex", comment = FALSE)
```

```{r exposuretab2, message = FALSE, cache = FALSE, results = 'asis'}
print(xtable(ex[,,1], label = "tab:menexp", caption = "Exposure in years by social class and period, men.", digits = 0), 
      type = "latex", comment = FALSE)
```

@@

```{r deathtab, message = FALSE, cache = FALSE, results = 'asis'}
##expo <- aggregate(vb[, c("exposure")], by = vb[, c("hisclass", "period", "sex")], FUN = sum)
deaths <- with(vb, tapply(event, list(period, hisclass, sex), sum))
print(xtable(deaths[,,2], label = "tab:womendeaths", caption = "Number of deaths by social class and period, women.", digits = 0), 
      type = "latex", comment = FALSE)
```

```{r deathtab2, message = FALSE, cache = FALSE, results = 'asis'}
print(xtable(deaths[,,1], label = "tab:mendeaths", caption = "Number of deaths by social class and period, men.", digits = 0), 
      type = "latex", comment = FALSE)
```
